---
title: "p8105_hw5_sc5351"
author: "Shaoyu Chen"
date: "2023-11-14"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 10, 
  fig.height = 8,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

#Describe the raw data. 
```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv", na = c("", "NA", "Unknown")) %>%
  mutate(
    city_state = str_c(city, state, sep = ", "),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )
  ) %>% 
  filter(city_state != "Tulsa, AL") 
```
#In the next code chunk, I group within cities and summarize to produce the total number of homicides and the number that are solved. 
```{r}
city_homicide_df = 
  homicide_df %>% 
  select(city_state, disposition, resolution) %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolution == "unsolved"))
```
#For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.
```{r}
bmore_test = 
  prop.test(
    x = filter(city_homicide_df, city_state == "Baltimore, MD") %>% pull(hom_unsolved),
    n = filter(city_homicide_df, city_state == "Baltimore, MD") %>% pull(hom_total)) 

broom::tidy(bmore_test) %>% 
  knitr::kable(digits = 3)
```
#Building on this code, I can use functions in the `purrr` package to obtain estimates and CIs for the proportion of unsolved homicides in each city in my dataset. The code below implements this analysis. 
```{r}
test_results = 
  city_homicide_df %>% 
  mutate(
    prop_tests = map2(hom_unsolved, hom_total, \(x, y) prop.test(x = x, n = y)),
    tidy_tests = map(prop_tests, broom::tidy)) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high) %>% 
  mutate(city_state = fct_reorder(city_state, estimate))
```

#Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r}
test_results %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

